Towards a Machine Learning approach for Aggregate Computing

### 2021-10-08 paper-2021-woa-ac-ml.tex
add code repository

To verify if we can improve the convergence time using reinforcement learning,
 we simulate a situation where the rising problem emerges:
 in the beginning, two source nodes exist in the network, ($\alpha$ and $\beta$).
 At the time $t$, $\beta$ disappears. So the node near to $\beta$ start a slow process
 to eventually reach the distance towards $\alpha$.
%
We use 80 nodes displaced into an irregular grid 100x20 meters. 
 Each node has a neighbourhoods range equal to 8 meters. 
 So, on average, each node has 7 neighbours.
 The time $t$ is fixed to 35.
 Each simulation least 120-time unit.
% 
We run the simulation for 100 episodes.
 The Q-learning parameters are:
$$
\epsilon = 0.01, 
\alpha_t = 0.05,
\gamma = 0.9
$$
\Cref{fig:simulation} shows the error for both naive implementation and Reinforcement Learning based implementation as time changes.
The error is evaluated as:
$$
error(i, t) \leftarrow  | \textit{rightValue}(i,t) - \textit{output}(i,t) |
$$
Where \textbf{i} is the node identifier and \textbf{t} is the time when the error is evaluated.
%
As you can see, at the time 100 using the greedy policy, the collective learning to recover to a stable situation
 faster than the standard naive implementation.

>>>>

To verify if we can improve the convergence time using reinforcement learning,
 we simulate a situation where the rising problem emerges (repository at \url{https://github.com/cric96/scafi-with-reinforcement-learning/tree/independent-q-learning-hop-count}):
 in the beginning, two source nodes exist in the network, ($\alpha$ and $\beta$).
 At the time $t$, $\beta$ disappears. So the node near to $\beta$ start a slow process
 to eventually reach the distance towards $\alpha$.
%
We use 80 nodes displaced into an irregular grid 100x20 meters. 
 Each node has a neighbourhoods range equal to 8 meters. 
 So, on average, each node has 7 neighbours.
 The time $t$ is fixed to 35.
 Each simulation least 120-time unit.
% 
We run the simulation for 100 episodes.
 The Q-learning parameters are:
$$
\epsilon = 0.01, 
\alpha_t = 0.05,
\gamma = 0.9
$$
\Cref{fig:simulation} shows the error for both naive implementation and Reinforcement Learning based implementation as time changes.
The error is evaluated as:
$$
error(i, t) \leftarrow  | \textit{rightValue}(i,t) - \textit{output}(i,t) |
$$
Where \textbf{i} is the node identifier and \textbf{t} is the time when the error is evaluated.
%
As you can see, at the time 100 using the greedy policy, the collective learning to recover to a stable situation
 faster than the standard naive implementation.
